Multi-dimensional Urban Network Percolation

### 2019-03-17 Docs/Papers/Percolation/paper/paper.tex
paper_submitted

\documentclass{article}
\pdfoutput=1 %forces arXiv/HAL to compile with PDFLaTeX

% Packages
\usepackage{array}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[margin=2.4cm]{geometry}

@@

\author{Juste RAIMBAULT$^{1,2,3,\ast}$\\
$^1$ UPS CNRS 3611 ISC-PIF, France\\
$^2$ CASA, UCL, UK\\
$^3$ UMR CNRS 8504 G{\'e}ographie-cit{\'e}s\\\medskip
$^{\ast}$ \texttt{juste.raimbault@polytechnique.edu}
}

\date{}

@@

\abstract{Network percolation has recently been proposed as a method to characterize the global structure of an urban system form the bottom-up. This paper proposes to extend urban network percolation in a multi-dimensional way, to take into account both urban form (spatial distribution of population) and urban functions (here as properties of transportation networks). The method is applied to the European urban system to reconstruct endogenous urban regions. The variable parametrization allows to consider patterns of optimization for two stylized contradictory sustainability indicators (economic performance and greenhouse gases emissions). This suggests a customizable spatial design of policies to develop sustainable territories.\\\medskip
\textbf{Keywords: } Road network; Multi-dimensional percolation; European urban system; Mega-city region
}

@@

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=\linewidth]{principle.pdf}}
  \centering
  \caption{Schematic representation of the multi-dimensional network percolation heuristic. We show a stylized configuration with two layers having the same nodes, and the links within each layer are created following the percolation radius $r_0$ and the thresholds for the layer variables. The final clusters are the superposition of these. The green points give examples of starting points in the case of a propagation heuristic.\label{fig:method}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

@@

In practice, the analysis is implemented using R and the igraph package. Source code, data and results are available on the open git repository of the project at \texttt{https://github.com/JusteRaimbault/UrbanMorphology}. The network is constructed by superposing the population density layer with the network layer, starting from the 5km resolution spatial fields for morphological and network indicators. This network is filtered with the threshold parameters for each layer and with the radius parameter. Connected components yield the clusters that we interpret as endogenous regions.

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=0.49\linewidth]{abssize_nodes.png}}
  {\includegraphics[width=0.49\linewidth]{relsize_nodes.png}}
  \centering
  \caption{Percolation transition. On the left, we plot the size of the largest cluster in each configuration in terms of nodes, as a function of the percolation radius $r_0$. Color gives the other percolation parameters. On the right, the plot is similar but with the size relative to the size of the largest cluster obtained with the maximal radius in each configuration.\label{fig:percolation}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=\linewidth]{fractaldimension.png}}
  \centering
  \caption{Fractal dimension. We plot for each parametrization given by the curve color the evolution of the fractal dimension $\alpha$ as a function of $r_0$. Standard errors are not plotted for readability.\label{fig:fractaldim}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!] 
%\resizebox{10cm}{7cm}
{\includegraphics[width=0.49\textwidth]{totalPop4183694_00056402_ecount850_radius8000.png}}
  {\includegraphics[width=0.49\linewidth]{totalPop2219780_36719597_vcount378_radius8000.png}}\\
  {\includegraphics[width=0.49\linewidth]{totalPop1474347_36891685_vcount595_radius50000.png}}
   {\includegraphics[width=0.49\linewidth]{totalPop1474347_36891685_euclPerf0_00507404608502498_radius54000.png}}
  \centering

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=0.7\linewidth]{full_effective_pareto.png}}
  \centering
  \caption{Point clouds of region-level indicators, namely population and emissions, for different parametrizations, given by the color. Each point represent an endogenous urban region.\label{fig:paretos}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=\linewidth]{aggreg_morpho_pc1-emissions_targeted.png}}
  \centering
  \caption{Aggregated values of normalized potential emissions $\sum_c \tilde{g}_c$, as a function of the first morphological principal component (PC1), for varying values of parameters $d_G$ (rows) and $\gamma_G$ (columns). Other intermediate values for these parameters yield similar behaviors. As PC1 is mainly linked to monocentricity, there seems to exist an optimal intermediate level of monocentricity for emissions alone. Color level give the share of population within the considered clusters in comparison to all European population.\label{fig:emissions-pc1}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=\linewidth]{aggreg_morpho_relemissions-relefficiency_colpc1_logscale_targeted.png}}
  \centering  
  \caption{Relative potential emissions $\sum_c g_c$ against relative potential economic unefficiency $\sum_c e_c$ (both indicators should be minimized), for varying values of $\gamma_G$ (columns) and $d_G$ (rows). Color level gives the value of PC1, whereas point size gives the share of total population contained within considered areas.\label{fig:paretos-relative}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

@@

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Arbabi, Mayfield, and McCann}{Arbabi
  \textit{et~al.}}{2019}]{arbabi2019development}
Arbabi H., Mayfield M., McCann P. (2019).
\newblock On the development logic of city-regions: inter-versus intra-city
  mobility in england and wales.
\newblock {\em Spatial Economic Analysis\/}, 1--20.

\bibitem[\protect\citeauthoryear{Arcaute, Molinero, Hatna, Murcio, Vargas-Ruiz,
  Masucci, and Batty}{Arcaute \textit{et~al.}}{2016}]{arcaute2016cities}
Arcaute E., Molinero C., Hatna E., Murcio R., Vargas-Ruiz C., Masucci A.~P.,
  Batty M. (2016).
\newblock Cities and regions in britain through hierarchical percolation.
\newblock {\em Royal Society open science\/}~{\em 3\/}(4), 150691.

\bibitem[\protect\citeauthoryear{Banos and Genre-Grandpierre}{Banos and
  Genre-Grandpierre}{2012}]{banos2012towards}
Banos A., Genre-Grandpierre C. (2012).
\newblock Towards new metrics for urban road networks: Some preliminary
  evidence from agent-based simulations.
\newblock In {\em Agent-based models of geographical systems}, pp.\  627--641.
  Springer.

\bibitem[\protect\citeauthoryear{Barth{\'e}lemy}{Barth{\'e}lemy}{2011}]{barthelemy2011spatial}
Barth{\'e}lemy M. (2011).
\newblock Spatial networks.
\newblock {\em Physics Reports\/}~{\em 499\/}(1-3), 1--101.

\bibitem[\protect\citeauthoryear{Batty and Longley}{Batty and
  Longley}{1994}]{batty1994fractal}
Batty M., Longley P.~A. (1994).
\newblock {\em Fractal cities: a geometry of form and function}.
\newblock Academic press.

\bibitem[\protect\citeauthoryear{Bettencourt, Lobo, Helbing, K{\"u}hnert, and
  West}{Bettencourt \textit{et~al.}}{2007}]{bettencourt2007growth}
Bettencourt L.~M., Lobo J., Helbing D., K{\"u}hnert C., West G.~B. (2007).
\newblock Growth, innovation, scaling, and the pace of life in cities.
\newblock {\em Proceedings of the national academy of sciences\/}~{\em
  104\/}(17), 7301--7306.

\bibitem[\protect\citeauthoryear{Boccaletti, Bianconi, Criado, Del~Genio,
  G{\'o}mez-Gardenes, Romance, Sendina-Nadal, Wang, and Zanin}{Boccaletti
  \textit{et~al.}}{2014}]{boccaletti2014structure}
Boccaletti S., Bianconi G., Criado R., Del~Genio C.~I., G{\'o}mez-Gardenes J.,
  Romance M., Sendina-Nadal I., Wang Z., Zanin M. (2014).
\newblock The structure and dynamics of multilayer networks.
\newblock {\em Physics Reports\/}~{\em 544\/}(1), 1--122.

\bibitem[\protect\citeauthoryear{Burger and Meijers}{Burger and
  Meijers}{2012}]{burger2012form}
Burger M., Meijers E. (2012).
\newblock Form follows function? linking morphological and functional
  polycentricity.
\newblock {\em Urban studies\/}~{\em 49\/}(5), 1127--1149.

\bibitem[\protect\citeauthoryear{Callaway, Newman, Strogatz, and
  Watts}{Callaway \textit{et~al.}}{2000}]{callaway2000network}
Callaway D.~S., Newman M.~E., Strogatz S.~H., Watts D.~J. (2000).
\newblock Network robustness and fragility: Percolation on random graphs.
\newblock {\em Physical review letters\/}~{\em 85\/}(25), 5468.

\bibitem[\protect\citeauthoryear{Cottineau, Finance, Hatna, Arcaute, and
  Batty}{Cottineau \textit{et~al.}}{2018}]{cottineau2018defining}
Cottineau C., Finance O., Hatna E., Arcaute E., Batty M. (2018).
\newblock Defining urban clusters to detect agglomeration economies.
\newblock {\em Environment and Planning B: Urban Analytics and City Science\/},
  2399808318755146.

\bibitem[\protect\citeauthoryear{Cottineau, Hatna, Arcaute, and
  Batty}{Cottineau \textit{et~al.}}{2017}]{cottineau2017diverse}
Cottineau C., Hatna E., Arcaute E., Batty M. (2017).
\newblock Diverse cities or the systematic paradox of urban scaling laws.
\newblock {\em Computers, environment and urban systems\/}~{\em 63}, 80--94.

\bibitem[\protect\citeauthoryear{Crucitti, Latora, and Porta}{Crucitti
  \textit{et~al.}}{2006}]{crucitti2006centrality}
Crucitti P., Latora V., Porta S. (2006).
\newblock Centrality measures in spatial networks of urban streets.
\newblock {\em Physical Review E\/}~{\em 73\/}(3), 036125.

\bibitem[\protect\citeauthoryear{Ducruet and Beauguitte}{Ducruet and
  Beauguitte}{2014}]{ducruet2014spatial}
Ducruet C., Beauguitte L. (2014).
\newblock Spatial science and network science: Review and outcomes of a complex
  relationship.
\newblock {\em Networks and Spatial Economics\/}~{\em 14\/}(3-4), 297--316.

\bibitem[\protect\citeauthoryear{Hackett, Cellai, G{\'o}mez, Arenas, and
  Gleeson}{Hackett \textit{et~al.}}{2016}]{hackett2016bond}
Hackett A., Cellai D., G{\'o}mez S., Arenas A., Gleeson J.~P. (2016).
\newblock Bond percolation on multiplex networks.
\newblock {\em Physical Review X\/}~{\em 6\/}(2), 021002.

\bibitem[\protect\citeauthoryear{Hall and Pain}{Hall and
  Pain}{2006}]{hall2006polycentric}
Hall P.~G., Pain K. (2006).
\newblock {\em The polycentric metropolis: learning from mega-city regions in
  Europe}.
\newblock Routledge.

\bibitem[\protect\citeauthoryear{Hillier, Leaman, Stansall, and
  Bedford}{Hillier \textit{et~al.}}{1976}]{hillier1976space}
Hillier B., Leaman A., Stansall P., Bedford M. (1976).
\newblock Space syntax.
\newblock {\em Environment and Planning B: Planning and design\/}~{\em 3\/}(2),
  147--185.

\bibitem[\protect\citeauthoryear{Huynh, Makarov, Legara, Monterola, and
  Chew}{Huynh \textit{et~al.}}{2018}]{huynh2018characterisation}
Huynh H.~N., Makarov E., Legara E.~F., Monterola C., Chew L.~Y. (2018).
\newblock Characterisation and comparison of spatial patterns in urban systems:
  A case study of us cities.
\newblock {\em Journal of computational science\/}~{\em 24}, 34--43.

\bibitem[\protect\citeauthoryear{Janssens-Maenhout, Crippa, Guizzardi, Muntean,
  Schaaf, Dentener, Bergamaschi, Pagliari, Olivier, Peters,
  \textit{et~al.}}{Janssens-Maenhout \textit{et~al.}}{2017}]{janssens2017edgar}
Janssens-Maenhout G., Crippa M., Guizzardi D., Muntean M., Schaaf E., Dentener
  F., Bergamaschi P., Pagliari V., Olivier J., Peters J., \textit{et~al.}
  (2017).
\newblock Edgar v4. 3.2 global atlas of the three major greenhouse gas
  emissions for the period 1970--2012.
\newblock {\em Earth Syst. Sci. Data Discuss\/}.

\bibitem[\protect\citeauthoryear{Komiyama and Takeuchi}{Komiyama and
  Takeuchi}{2006}]{komiyama2006sustainability}
Komiyama H., Takeuchi K. (2006).
\newblock {\em Sustainability science: building a new discipline}.

\bibitem[\protect\citeauthoryear{Lagesse, Bordin, and Douady}{Lagesse
  \textit{et~al.}}{2015}]{lagesse2015spatial}
Lagesse C., Bordin P., Douady S. (2015).
\newblock A spatial multi-scale object to analyze road networks.
\newblock {\em Network Science\/}~{\em 3\/}(1), 156--181.

\bibitem[\protect\citeauthoryear{Lashof and Ahuja}{Lashof and
  Ahuja}{1990}]{lashof1990relative}
Lashof D.~A., Ahuja D.~R. (1990).
\newblock Relative contributions of greenhouse gas emissions to global warming.
\newblock {\em Nature\/}~{\em 344\/}(6266), 529.

\bibitem[\protect\citeauthoryear{Le~N{\'e}chet}{Le~N{\'e}chet}{2017}]{lenechet2017peupler}
Le~N{\'e}chet F. (2017).
\newblock De l'{\'e}talement urbain aux r{\'e}gions m{\'e}tropolitaines
  polycentriques : formes de fonctionnement et formes de gouvernance.
\newblock In {\em {Peupler la terre - De la pr{\'e}histoire {\`a} l'{\`e}re des
  m{\'e}tropoles}}. Presses Universitaires Francois Rabelais.

\bibitem[\protect\citeauthoryear{Louf and Barthelemy}{Louf and
  Barthelemy}{2013}]{louf2013modeling}
Louf R., Barthelemy M. (2013).
\newblock Modeling the polycentric transition of cities.
\newblock {\em Physical review letters\/}~{\em 111\/}(19), 198702.

\bibitem[\protect\citeauthoryear{Makse, Andrade, Batty, Havlin, Stanley,
  \textit{et~al.}}{Makse \textit{et~al.}}{1998}]{makse1998modeling}
Makse H.~A., Andrade J.~S., Batty M., Havlin S., Stanley H.~E., \textit{et~al.}
  (1998).
\newblock Modeling urban growth patterns with correlated percolation.
\newblock {\em Physical Review E\/}~{\em 58\/}(6), 7054.

\bibitem[\protect\citeauthoryear{McNally}{McNally}{2000}]{mcnally2000four}
McNally M.~G. (2000).
\newblock The four step model.

\bibitem[\protect\citeauthoryear{Newman and Watts}{Newman and
  Watts}{1999}]{newman1999scaling}
Newman M.~E., Watts D.~J. (1999).
\newblock Scaling and percolation in the small-world network model.
\newblock {\em Physical review E\/}~{\em 60\/}(6), 7332.

\bibitem[\protect\citeauthoryear{Penrose}{Penrose}{1999}]{penrose1999k}
Penrose M.~D. (1999).
\newblock On k-connectivity for a geometric random graph.
\newblock {\em Random Structures \& Algorithms\/}~{\em 15\/}(2), 145--164.

\bibitem[\protect\citeauthoryear{Perez, Banos, and Pettit}{Perez
  \textit{et~al.}}{2016}]{perez2016agent}
Perez P., Banos A., Pettit C. (2016).
\newblock Agent-based modelling for urban planning current limitations and
  future trends.
\newblock In {\em International Workshop on Agent Based Modelling of Urban
  Systems}, pp.\  60--69. Springer.

\bibitem[\protect\citeauthoryear{Piovani, Molinero, and Wilson}{Piovani
  \textit{et~al.}}{2017}]{piovani2017urban}
Piovani D., Molinero C., Wilson A. (2017).
\newblock Urban retail location: insights from percolation theory and spatial
  interaction modeling.
\newblock {\em PloS one\/}~{\em 12\/}(10), e0185787.

\bibitem[\protect\citeauthoryear{Raimbault}{Raimbault}{2018a}]{raimbault2018calibration}
Raimbault J. (2018a).
\newblock Calibration of a density-based model of urban morphogenesis.
\newblock {\em PloS one\/}~{\em 13\/}(9), e0203516.

\bibitem[\protect\citeauthoryear{Raimbault}{Raimbault}{2018b}]{raimbault2018caracterisation}
Raimbault J. (2018b).
\newblock {\em Caract{\'e}risation et mod{\'e}lisation de la co-{\'e}volution
  des r{\'e}seaux de transport et des territoires}.
\newblock Ph.\ D. thesis, Universit{\'e} Paris 7 Denis Diderot.

\bibitem[\protect\citeauthoryear{Raimbault}{Raimbault}{2018c}]{raimbault2018indirect}
Raimbault J. (2018c).
\newblock Indirect evidence of network effects in a system of cities.
\newblock {\em Environment and Planning B: Urban Analytics and City Science\/},
  2399808318774335.

\bibitem[\protect\citeauthoryear{Raimbault}{Raimbault}{2019}]{raimbault2018urban}
Raimbault J. (2019).
\newblock An urban morphogenesis model capturing interactions between networks
  and territories.
\newblock In {\em The Mathematics of Urban Morphology, D'acci L., ed., Springer
  Birkhauser Mathematics}.

\bibitem[\protect\citeauthoryear{Reuillon, Leclaire, and
  Rey-Coyrehourcq}{Reuillon \textit{et~al.}}{2013}]{reuillon2013openmole}
Reuillon R., Leclaire M., Rey-Coyrehourcq S. (2013).
\newblock Openmole, a workflow engine specifically tailored for the distributed
  exploration of simulation models.
\newblock {\em Future Generation Computer Systems\/}~{\em 29\/}(8), 1981--1990.

\bibitem[\protect\citeauthoryear{Sanders}{Sanders}{2017}]{sanders2017peupler}
Sanders L. (2017).
\newblock {\em Peupler la terre - De la pr{\'e}histoire {\`a} l'{\`e}re des
  m{\'e}tropoles.}
\newblock Presses Universitaires Francois Rabelais.

\bibitem[\protect\citeauthoryear{Son, Bizhani, Christensen, Grassberger, and
  Paczuski}{Son \textit{et~al.}}{2012}]{son2012percolation}
Son S.-W., Bizhani G., Christensen C., Grassberger P., Paczuski M. (2012).
\newblock Percolation theory on interdependent networks based on epidemic
  spreading.
\newblock {\em EPL (Europhysics Letters)\/}~{\em 97\/}(1), 16006.

\bibitem[\protect\citeauthoryear{Stauffer and Aharony}{Stauffer and
  Aharony}{2014}]{stauffer2014introduction}
Stauffer D., Aharony A. (2014).
\newblock {\em Introduction to percolation theory}.
\newblock Taylor \& Francis.

\bibitem[\protect\citeauthoryear{Tammaru, Marci{\'n}czak, Van~Ham, and
  Musterd}{Tammaru \textit{et~al.}}{2015}]{tammaru2015multi}
Tammaru T., Marci{\'n}czak S., Van~Ham M., Musterd S. (2015).
\newblock A multi-factor approach to understanding socio-economic segregation
  in european capital cities.
\newblock In {\em Socio-economic segregation in European capital cities}, pp.\
  25--53. Routledge.

\bibitem[\protect\citeauthoryear{Tobler}{Tobler}{2004}]{tobler2004first}
Tobler W. (2004).
\newblock On the first law of geography: A reply.
\newblock {\em Annals of the Association of American Geographers\/}~{\em
  94\/}(2), 304--310.

\bibitem[\protect\citeauthoryear{Vigui{\'e} and Hallegatte}{Vigui{\'e} and
  Hallegatte}{2012}]{viguie2012trade}
Vigui{\'e} V., Hallegatte S. (2012).
\newblock Trade-offs and synergies in urban climate policies.
\newblock {\em Nature Climate Change\/}~{\em 2\/}(5), 334.

\end{thebibliography}

>>>>

\documentclass{jimis-en}
\pdfoutput=1 %forces arXiv/HAL to compile with PDFLaTeX

% Packages
\usepackage{array}
\usepackage{pgfplots}
\usepackage{graphicx}

\author[1,2,3,*]{Juste RAIMBAULT}
\affil[1]{UPS CNRS 3611 ISC-PIF, France} 
\affil[2]{CASA, UCL, UK}
\affil[3]{UMR CNRS 8504 G{\'e}ographie-cit{\'e}s}

% corresponding author with his/her email
\corrauthor{juste.raimbault@polytechnique.edu}

%% Information provided by JIMIS:
%ISSN
% DOI 
\doi{10.18713/JIMIS-ddmmyy-v-a}{}
% reviewing process: first date = submission, second date = acceptance 
\review{Month-in-letters Day Year}{Month-in-letters Day Year}
% Volume and Year of the issue
\publication{N}{YYYY}

%% Information provided by the Editors:
% Issue Title 
\issue{Title of the interdisciplinary issue}
% List of k Editors
\editors{}

@@

@@

\abstract{Network percolation has recently been proposed as a method to characterize the global structure of an urban system form the bottom-up. This paper proposes to extend urban network percolation in a multi-dimensional way, to take into account both urban form (spatial distribution of population) and urban functions (here as properties of transportation networks). The method is applied to the European urban system to reconstruct endogenous urban regions. The variable parametrization allows to consider patterns of optimization for two stylized contradictory sustainability indicators (economic performance and greenhouse gases emissions). This suggests a customizable spatial design of policies to develop sustainable territories.}

\keywords{Road network; Multi-dimensional percolation; European urban system; Mega-city region}

@@

\strut
\vspace{-4ex}

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=\linewidth]{figures/principle.pdf}}
  \centering
  \caption{Schematic representation of the multi-dimensional network percolation heuristic. We show a stylized configuration with two layers having the same nodes, and the links within each layer are created following the percolation radius $r_0$ and the thresholds for the layer variables. The final clusters are the superposition of these. The green points give examples of starting points in the case of a propagation heuristic.\label{fig:method}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

@@

In practice, the analysis is implemented using R and the igraph package. Source code, data and results are available on the open git repository of the project at \url{https://github.com/JusteRaimbault/UrbanMorphology}. The network is constructed by superposing the population density layer with the network layer, starting from the 5km resolution spatial fields for morphological and network indicators. This network is filtered with the threshold parameters for each layer and with the radius parameter. Connected components yield the clusters that we interpret as endogenous regions.

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=0.49\linewidth]{figures/abssize_nodes.png}}
  {\includegraphics[width=0.49\linewidth]{figures/relsize_nodes.png}}
  \centering
  \caption{Percolation transition. On the left, we plot the size of the largest cluster in each configuration in terms of nodes, as a function of the percolation radius $r_0$. Color gives the other percolation parameters. On the right, the plot is similar but with the size relative to the size of the largest cluster obtained with the maximal radius in each configuration.\label{fig:percolation}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=\linewidth]{figures/fractaldimension.png}}
  \centering
  \caption{Fractal dimension. We plot for each parametrization given by the curve color the evolution of the fractal dimension $\alpha$ as a function of $r_0$. Standard errors are not plotted for readability.\label{fig:fractaldim}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!] 
%\resizebox{10cm}{7cm}
{\includegraphics[width=0.49\textwidth]{figures/totalPop4183694_00056402_ecount850_radius8000.png}}
  {\includegraphics[width=0.49\linewidth]{figures/totalPop2219780_36719597_vcount378_radius8000.png}}\\
  {\includegraphics[width=0.49\linewidth]{figures/totalPop1474347_36891685_vcount595_radius50000.png}}
   {\includegraphics[width=0.49\linewidth]{figures/totalPop1474347_36891685_euclPerf0_00507404608502498_radius54000.png}}
  \centering

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=0.7\linewidth]{figures/full_effective_pareto.png}}
  \centering
  \caption{Point clouds of region-level indicators, namely population and emissions, for different parametrizations, given by the color. Each point represent an endogenous urban region.\label{fig:paretos}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=\linewidth]{figures/aggreg_morpho_pc1-emissions_targeted.png}}
  \centering
  \caption{Aggregated values of normalized potential emissions $\sum_c \tilde{g}_c$, as a function of the first morphological principal component (PC1), for varying values of parameters $d_G$ (rows) and $\gamma_G$ (columns). Other intermediate values for these parameters yield similar behaviors. As PC1 is mainly linked to monocentricity, there seems to exist an optimal intermediate level of monocentricity for emissions alone. Color level give the share of population within the considered clusters in comparison to all European population.\label{fig:emissions-pc1}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!ht] 
%\resizebox{10cm}{7cm}
  {\includegraphics[width=\linewidth]{figures/aggreg_morpho_relemissions-relefficiency_colpc1_logscale_targeted.png}}
  \centering  
  \caption{Relative potential emissions $\sum_c g_c$ against relative potential economic unefficiency $\sum_c e_c$ (both indicators should be minimized), for varying values of $\gamma_G$ (columns) and $d_G$ (rows). Color level gives the value of PC1, whereas point size gives the share of total population contained within considered areas.\label{fig:paretos-relative}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

@@

\bibliographystyle{jimis-en}
\bibliography{biblio}
